Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages

### 2019-04-22 sattose/paper.tex
Something about categories and measurements

\subsection{Relations Between Clone Instances}
When merging code clones in object-oriented languages, it is very important to consider the relation between clone instances. A paper by Fontana et al \cite{fontana2015duplicated} performs measurements on 50 open source projects on the relation of clones to each other. To do this, they first define several categories for the relation between clone instances in object-oriented languages. These categories are as follows:
\begin{enumerate}
  \item \textbf{Same method}: All instances of the clone class are in the same method.
  \item \textbf{Same class}: All instances of the clone class are in the same class.
  \item \textbf{Superclass}: All instances of the clone class are children and parents of each other.
  \item \textbf{Ancestor class}: All instances of the clone class are superclasses except for the direct superclass.
  \item \textbf{Sibling class}: All instances of the clone class have the same parent class.
  \item \textbf{First cousin class}: All instances of the clone class have the same grandparent class.
\item \textbf{Common hierarchy class}: All instances of the clone class belong to the same hierarchy, but do not belong to any of the other categories.
\item \textbf{Same external superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
\end{enumerate}
Please note that no of these categories allow external classes (except for ``same external superclass''). So if two clone instances are related through external classes but do not share a common external superclass, it will be flagged as ``unrelated''. The main reason for this is that it is (often) not possible to refactor to external classes.

@@

>>>>

\subsection{Relations Between Clone Instances}
When merging code clones in object-oriented languages, it is very important to consider the relation between clone instances.

\subsubsection{Categorizing Clone Instance Relations}
A paper by Fontana et al \cite{fontana2015duplicated} performs measurements on 50 open source projects on the relation of clones to each other. To do this, they first define several categories for the relation between clone instances in object-oriented languages. These categories are as follows:
\begin{enumerate}
  \item \textbf{Same method}: All instances of the clone class are in the same method.
  \item \textbf{Same class}: All instances of the clone class are in the same class.
  \item \textbf{Superclass}: All instances of the clone class are children and parents of each other.
  \item \textbf{Ancestor class}: All instances of the clone class are superclasses except for the direct superclass.
  \item \textbf{Sibling class}: All instances of the clone class have the same parent class.
  \item \textbf{First cousin class}: All instances of the clone class have the same grandparent class.
\item \textbf{Common hierarchy class}: All instances of the clone class belong to the same hierarchy, but do not belong to any of the other categories.
\item \textbf{Same external superclass}: All instances of the clone class have the same superclass, but this superclass is not included in the project but part of a library.
\item \textbf{Unrelated class}: There is at least one instance in the clone class that is not in the same hierarchy.
\end{enumerate}
Please note that no of these categories allow external classes (except for ``same external superclass''). So if two clone instances are related through external classes but do not share a common external superclass, it will be flagged as ``unrelated''. The main reason for this is that it is (often) not possible to refactor to external classes.

@@

\subsubsection{Our measurements}
We have recreated the same table as Fontana et al \cite{fontana2015duplicated}, but with the following differences:
\begin{itemize}
  \item We consider clone classes rather than clone pairs
\item We use different thresholds regarding when a clone should be considered.
\item We seek by statement/declaration rather than SLOC.
\item We test a broader range of projects (they a set of 50 relatively large projects, we use a large corpus that was assembled by a machine learning algorithm testing java projects on GitHub for quality, which contains projects of all sizes and with differing code quality)
\end{itemize}
